Real-time resolution of short-read assembly graph using ONT long reads

### 2020-08-12 plos_latex_edit.tex
edit intro for motivation

Sequencing technology has reached a level of maturity which allows the decoding of virtually any piece of genetic material
which  can be obtained. 
%This provides the potential use of DNA sequencing into a wide range of applications in medical 
%and scientific research. 
However, the time from sample to result remains a barrier to adoption of 
sequencing technology into time critical applications such as infectious disease diagnostics or clinical decision making.  While
there exists real-time sequencing technology such as Oxford Nanopore Technologies (ONT);  algorithms for streaming analyses  of such real-time data are still
in their infancy. Effective streaming methodology will help bridge the gap between potential and practical use.

One particular strength of ONT technology is the production of ultra long reads. This is complementary to the dominant
short read sequencing technology Illumina which is cheaper and has higher per base read quality
but is unable to resolve the complex regions of the genome due to its read length limitation. A natural combination of
the two technologies is in hybrid assembly of genomes. Previously, we developed \npscarf{}~\cite{Cao2017scaffolding} an algorithm to 
scaffold a draft assembly from Illumina sequencing simultaneously with ONT sequencing.  However, \npscarf{} ignores the rich  connectivity information in the short read assembly graph, and as a result is prone to mis-assembly.
%The strategy proved to be
%a time- and cost- effective methodology where practitioners need to generate only sufficient data for completing 
%a draft genome.

@@

@@

\bibitem{Potter2016rapid}
Potter RF, D’souza AW, Dantas G.
\newblock {The rapid spread of carbapenem-resistant Enterobacteriaceae}.
\newblock Drug Resistance Updates. 2016;29:30--46.

@@

\bibitem{Giordano2017}
Giordano F, Aigrain L, Quail MA, Coupland P, Bonfield JK, Davies RM, et~al.
\newblock {De novo yeast genome assemblies from MinION, PacBio and MiSeq
  platforms}.
\newblock Scientific reports. 2017;7(1):3935.

\bibitem{Prjibelski2014}
Prjibelski AD, Vasilinetc I, Bankevich A, Gurevich A, Krivosheeva T, Nurk S,
  et~al.
\newblock {ExSPAnder}: a universal repeat resolver for {DNA} fragment assembly.
\newblock Bioinformatics. 2014;30(12):i293--i301.

\bibitem{Qin2019}
Qin, M., Wu, S., Li, A., Zhao, F., Feng, H., Ding, L., Ruan, J
\newblock {{LRScaf}: improving draft genomes using long noisy reads}
\newblock BMC Genomics. 2019;20(1):955
\end{thebibliography}

\end{document}

>>>>

Sequencing technology has reached a level of maturity which allows the decoding of virtually any piece of genetic material which  can be obtained. 
%This provides the potential use of DNA sequencing into a wide range of applications in medical 
%and scientific research. 
However, the time from sample to result remains a barrier to adoption of sequencing technology into time critical applications such as infectious disease diagnostics or clinical decision making. 
While there exists real-time sequencing technology such as Oxford Nanopore Technologies (ONT), algorithms for streaming analyses of such real-time data are still in their infancy. Effective streaming methodology will help bridge the gap between potential and practical use. 
\addnew{In addition, the release of Read Until API enables direct control to the actual molecular reading process which has paved the way for customized selective and/or enrichment sequencing on ONT platforms. To function properly, methods using this protocol must implement rapid-responsed operations on the streaming data, for example in ReadFish~\cite{Payne2020}.}

One particular strength of ONT technology is the production of ultra long reads. 
This is complementary to the dominant short read sequencing technology Illumina which is cheaper and has higher per base read quality but is unable to resolve the complex regions of the genome due to its read length limitation. 
A natural combination of the two technologies is in hybrid assembly of genomes. Previously, we developed \npscarf{}~\cite{Cao2017scaffolding} an algorithm to scaffold a draft assembly from Illumina sequencing simultaneously with ONT sequencing.  However, \npscarf{} ignores the rich connectivity information in the short read assembly graph, and as a result is relatively prone to mis-assembly compared to alternative methods.
%The strategy proved to be
%a time- and cost- effective methodology where practitioners need to generate only sufficient data for completing 
%a draft genome.

@@

\bibitem{Payne2020}
Payne A, Holmes N, Clarke T, Munro R, Debebe B, Loose M.
\newblock Nanopore adaptive sequencing for mixed samples, whole exome capture and targeted panels.
\newblock bioRxiv 2020.02.03.926956; 
\newblock doi: https://doi.org/10.1101/2020.02.03.926956

@@

\bibitem{Potter2016rapid}
Potter RF, D’souza AW, Dantas G.
\newblock The rapid spread of carbapenem-resistant \emph{Enterobacteriaceae}.
\newblock Drug Resistance Updates. 2016;29:30--46.

@@

\bibitem{Giordano2017}
Giordano F, Aigrain L, Quail MA, Coupland P, Bonfield JK, Davies RM, et~al.
\newblock De novo yeast genome assemblies from MinION, PacBio and MiSeq platforms.
\newblock Scientific reports. 2017;7(1):3935.

\bibitem{Prjibelski2014}
Prjibelski AD, Vasilinetc I, Bankevich A, Gurevich A, Krivosheeva T, Nurk S,
  et~al.
\newblock ExSPAnder: a universal repeat resolver for DNA fragment assembly.
\newblock Bioinformatics. 2014;30(12):i293--i301.

\bibitem{Qin2019}
Qin M, Wu S, Li A, Zhao F, Feng H, Ding L, Ruan J.
\newblock LRScaf: improving draft genomes using long noisy reads.
\newblock BMC Genomics. 2019;20(1):955

\end{thebibliography}
\end{document}
